Simulation for generic Cormotif model

### 2017-09-25 analysis/Simulation_generic_Cormotif.Rmd
wflow_publish("Simulation_generic_Cormotif.Rmd")

```{r,cache=TRUE}
fit$bic
```

$K = 4$ has the smallest BIC. The standard deviation built by our method is

```{r,cache=TRUE}
fit$mixsd
```

@@

```{r,cache=TRUE}
fit$bestmotif$pi
```

@@

```{r,cache=TRUE}
fit$bestmotif$W[[1]]
```

@@

```{r,cache=TRUE}
fit$bestmotif$W[[2]]
```

@@

```{r,cache=TRUE}
fit$bestmotif$W[[3]]
```

@@

```{r,cache=TRUE}
fit$bestmotif$W[[4]]
```

@@

```{r,cache=TRUE}
head(cbind(fit$result[[1]]$lfdr,fit$result[[2]]$lfdr,fit$result[[3]]$lfdr,fit$result[[4]]$lfdr))
```

@@

```{r,cache=TRUE}
head(cbind(fit$result[[1]]$lfsr,fit$result[[2]]$lfsr,fit$result[[3]]$lfsr,fit$result[[4]]$lfsr))
```

>>>>

```{r}
fit$bic
```

$K = 4$ has the smallest BIC. The standard deviation $\sigma_0,\sigma_1,\ldots,\sigma_L$ built by our method is

```{r}
fit$mixsd
```

@@

```{r}
fit$bestmotif$pi
```

@@

```{r}
fit$bestmotif$W[[1]]
```

@@

```{r}
fit$bestmotif$W[[2]]
```

@@

```{r}
fit$bestmotif$W[[3]]
```

@@

```{r}
fit$bestmotif$W[[4]]
```

@@

```{r}
head(cbind(fit$result[[1]]$lfdr,fit$result[[2]]$lfdr,fit$result[[3]]$lfdr,fit$result[[4]]$lfdr))
```

@@

```{r}
head(cbind(fit$result[[1]]$lfsr,fit$result[[2]]$lfsr,fit$result[[3]]$lfsr,fit$result[[4]]$lfsr))
```
